Results

### 2018-04-07 02_analysis.Rmd
Move helper functions out

  if (is.numeric(x)) {
    numeric_summary(x, variable)
  } else {
    level_summary(x, variable, df)
  }
}

if (isTRUE(getOption('knitr.in.progress'))) {
  file_format <- rmarkdown::all_output_formats(knitr::current_input())
} else {
  file_format <- ""
}

print_hux <- function(x) {
  if ("html_document" %in% file_format) {
    print_html(x)
  } else if ("pdf_document" %in% file_format) {
    print_latex(x)
  } else if ("word_document" %in% file_format) {
    print_md(x)
  } else {
    print(x)
  }
}

mcmc_pairwise_diffs <- function(chains) {
  # Calculate the pairwise differences between columns
  # Adapted from http://stackoverflow.com/a/28187446/120898
  pair_names <- outer(colnames(chains), colnames(chains),
                      paste, sep = " − ")
  pairs_to_omit <- which(lower.tri(pair_names, diag = TRUE))

  mcmc_diffs <- outer(1:ncol(chains), 1:ncol(chains),
                      function(x, y) chains[,x] - chains[,y]) %>% 
    magrittr::set_colnames(pair_names) %>% 
    select(-pairs_to_omit)

  return(mcmc_diffs)
}

tidy_diffs <- function(diffs_pairs) {
  diffs_pairs %>% 
    gather(pair, value) %>% 
    group_by(pair) %>% 
    summarise(mean = mean(value),
              median = median(value),
              q2.5 = quantile(value, probs = 0.025),
              q5 = quantile(value, probs = 0.05),
              q25 = quantile(value, probs = 0.25),
              q75 = quantile(value, probs = 0.75),
              q95 = quantile(value, probs = 0.95),
              q97.5 = quantile(value, probs = 0.975),
              p.greater0 = mean(value > 0),
              p.less0 = mean(value < 0),
              p.diff.not0 = ifelse(median > 0, p.greater0, p.less0))
}
```

# Miscellaneous details

## Average time to complete survey

```{r avg-time}
results %>% summarize(min = min(duration),
                      max = max(duration),
                      mean = mean(duration),
                      sd = sd(duration),
                      median = median(duration))
```

>>>>

  if (is.numeric(x)) {
    numeric_summary(x, variable)
  } else {
    level_summary(x, variable, df)
  }
}
```
